{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-06-02 sftrends_manu.Rnw
USGS refs to outline

\begin{enumerate}
\item How and why are trends interpreted - assessment of raw data, surrogates, various methods (kendall, GAM, WRTDS), what have been implications of using different approaches
\item WRTDS, original method
\item WRTDS application to Tampa Bay as test set, further validation in Patuxent
\item SF estuary, unique and prominent location, full story is eomplex (historical context and recent changes), no one has empirically described the data, how is this related to the delta (a vigorous biogeochemical reactor)
\item Study goal and objectives
\begin{itemize}
\item Provide a description of trends - annual, seasonal, spatial, response to flow, change by analytes
\item Detailed description of selected sites in the context of conceptual relationships - 1) nonlinear or extreme quantile changes, site TBD, 2) P8 and WWTP improvements, 3) Suisun DIN, SiO2, Chla, and clams
\item What this means for understanding other systems
\end{itemize}
\end{enumerate}

>>>>

\begin{enumerate}
\item How and why are trends interpreted - assessment of raw data, surrogates, various methods (kendall, GAM, WRTDS), what have been implications of using different approaches, see Kratzer USGS report http://pubs.usgs.gov/sir/2010/5228/pdf/sir20105228.pdf and data http://pubs.usgs.gov/sir/2010/5228/
\item WRTDS, original method
\item WRTDS application to Tampa Bay as test set, further validation in Patuxent
\item SF estuary, unique and prominent location, full story is eomplex (historical context and recent changes), no one has empirically described the data, how is this related to the delta (a vigorous biogeochemical reactor)
\item Study goal and objectives
\begin{itemize}
\item Provide a description of trends - annual, seasonal, spatial, response to flow, change by analytes
\item Detailed description of selected sites in the context of conceptual relationships - 1) nonlinear or extreme quantile changes, site TBD, 2) P8 and WWTP improvements, 3) Suisun DIN, SiO2, Chla, and clams
\item What this means for understanding other systems
\end{itemize}
\end{enumerate}
